Baseline Drift Estimation for Air Quality Data Using Quantile Trend Filtering

### 2019-04-17 Manuscript/detrendify_aoas.tex
changed to eBIC
added references to figures

 The solution to \Eqn{quantile_windows} is {\em not} identical to the solution to \Eqn{noncross_trend} because of double counting of the overlapping sections. The solutions are very close, however, and the differences are essentially immaterial concerning downstream analysis.

@@

\begin{figure}
	\centering
	\includegraphics[width = 0.8\linewidth]{Figures/admm_windows.png}
	\caption{Trend fit with our ADMM algorithm with 3 windows which converged in 7 iterations compared to trend from simultaneous fit. \Halley{Eric}{Need to reference in the text.}}
\end{figure}

@@

Our \texttt{detrend\_BIC} method performs the best overall in terms of both RMSE and CAA. While \texttt{qsreg} was competitive with our method in some cases, in the majority of cases the largest CAA values for each threshold were produced using the \texttt{detrend\_eBIC} method with the 1\textsuperscript{st} or 5\textsuperscript{th} quantiles.

\begin{figure}[h!]
	\includegraphics[width = \linewidth]{Figures/peaks_eg_class.png}
	\caption{Example signal classification using threshold. Red indicates true signal $(\VE{y}{i} - \VE{\theta}{i} > 0.5)$, blue indicates observations classified as signal after baseline removal using \texttt{detrend\_eBIC} and a threshold of 1.2. \Halley{Eric}{Need to explain what the threshold of 1.2 is.}}
	\label{fig:peaks_class_eg}
\end{figure}

\begin{figure}[h!]
	\includegraphics[width = \linewidth]{Figures/peaks_CAA.png}
	\caption{Class averaged accuracy by threshold, data size, and method (1 is best 0.5 is worst). \Halley{Eric}{Need to reference in the text.}}
\end{figure}

>>>>

 The solution to \Eqn{quantile_windows} is {\em not} identical to the solution to \Eqn{noncross_trend} because of double counting of the overlapping sections. The solutions are very close, however, and the differences are essentially immaterial concerning downstream analysis. \Fig{windowsfit} provides an illustration of trends estimated using \Alg{admm} and multiple windows compared with the trends estimated using a single window.

 \begin{figure}
 	\centering
 	\includegraphics[width = 0.8\linewidth]{Figures/admm_windows.png}
 	\caption{Trend fit with our ADMM algorithm with 3 windows which converged in 7 iterations compared to trend from simultaneous fit.} 
 	\label{fig:windowsfit}
 \end{figure}

@@

@@

Our \texttt{detrend\_eBIC} method performs the best overall in terms of both RMSE (\Fig{peaks_rmse}) and CAA (\Fig{CAA}). While \texttt{qsreg} was competitive with our method in some cases, in the majority of cases the largest CAA values for each threshold were produced using the \texttt{detrend\_eBIC} method with the 1\textsuperscript{st} or 5\textsuperscript{th} quantiles.

\begin{figure}[h!]
	\includegraphics[width = \linewidth]{Figures/peaks_eg_class.png}
	\caption{Example signal classification using threshold. Red indicates true signal $(\VE{y}{i} - \VE{\theta}{i} > 0.5)$, blue indicates observations classified as signal, i.e. values greater than 1.2 after baseline removal using \texttt{detrend\_eBIC}.}
	\label{fig:peaks_class_eg}
\end{figure}

\begin{figure}[h!]
	\includegraphics[width = \linewidth]{Figures/peaks_CAA.png}
	\caption{Class averaged accuracy by threshold, data size, and method (1 is best 0.5 is worst).}
	\label{fig:CAA}
\end{figure}
